---
title: "Stringency of Country Responses"
author: "Rebecca Xi"
date: "4/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(readr)
library(rvest)
library(janitor)
library(skimr)
library(sf)
library(maps)
library(tibble)
library(countrycode)
library(rworldmap)
library(gganimate)

options(scipen = 999)

```

```{r oxford data, include=FALSE}

# https://github.com/OxCGRT/covid-policy-tracker

# Import and clean Oxford Covid-Policy-Tracker data. Both sets are downloaded
# here, but we will likely only need the first (the second is for our own
# reference, as it contains detailed explanatory notes).

oxford <- read.csv(url("https://raw.githubusercontent.com/OxCGRT/covid-policy-tracker/master/data/OxCGRT_latest.csv")) %>% 
  mutate(new_date = as.Date(as.character(Date), format = "%Y%m%d"))

# oxford_detailed <- read.csv(url("https://raw.githubusercontent.com/OxCGRT/covid-policy-tracker/master/data/OxCGRT_latest_withnotes.csv"))
```

FYI: (see https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-031-v4.0_0.pdf for more info)

S1-S6 are further classified as either “targeted” (meaning they apply only in a
geographically concentrated area) or “general” (meaning they apply throughout the
entire jurisdiction).

### S1: School closing (Record closings of schools and universities)
0 - no measures
1 - recommend closing
2 - require closing

### S2: Workplace closing (Record closings of workplaces)
0 - No measures
1 - recommend closing
2 - require closing

### S3: Cancel public events (Record cancelling public events)
0 - No measures
1 - Recommend cancelling
2 - Require cancelling

### S4: Close public transport (Record closing of public transport)
0 - No measures
1 - Recommend closing
2 - Require closing

### S5: Public info campaigns (Record presence of public info campaigns)
0 -No COVID-19 public information campaign
1 - COVID-19 public information campaign

### s6: Restrictions on internal movement (Record restrictions on internal movement)
0 - No measures
1 - recommend movement restriction
2 - restrict movement

### s7: International travel controls (Record restrictions on international travel)
0 - No measures
1 - Screening
2 - Quarantine on high-risk regions
3 - Ban on high-risk regions

### s8: Fiscal measures (What economic stimulus policies are adopted?)
Value of fiscal stimuli, including spending or tax cuts (in USD)

### s9: Monetary measures (What monetary policy interventions?)
Value of interest rate (in %)

### s10: Emergency investment in healthcare (Short-term spending on, e.g, hospitals, masks,etc)
Value of new short-term spending on health (in USD)

### s11: Investment in vaccines (Announced public spending on vaccine development)
Value of investment (in USD)

### S12: Testing policy (Who can get tested)
0 - No testing policy
1 - only testing those who both (a) have symptoms, and (b) meet specific criteria (eg key workers, admitted to hospital, came into contact with a known case, returned from overseas)
2 - testing of anyone showing COVID19 symptoms 
3 - open public testing (eg “drive through” testing available to asymptomatic people)

###S13: Contact tracing (Are governments doing contact tracing)
0 - no contact tracing
1 - limited contact tracing – not done for all cases
2 - comprehensive contact tracing – done for all cases


```{r JHU data, include=FALSE}

# Read in and clean global JHU CSSE data. Update the date format and create an
# increment column for the confirmed cases across the globe

# Confirmed

global_confirmed <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")) %>% 
  clean_names() %>% 
  pivot_longer(cols = -c(province_state, country_region, lat, long), names_to = "date", values_to = "confirmed") %>%
  select(province_state, country_region, date, confirmed)

global_confirmed <- global_confirmed %>% 
  mutate(sep_date = sub("x", "", date)) %>%
  mutate(new_date = as.Date(sep_date, format = "%m_%d_%y")) %>%
  group_by(country_region, new_date) %>%
  summarize(confirmed = sum(confirmed)) 

#%>%
#ungroup() %>%
#mutate(helper = c(
#confirmed[1],
    #confirmed[1:(nrow(.) - 1)])
  #) %>%
  #mutate(increment = confirmed - helper) 
  


# Deaths

global_deaths <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")) %>% 
  clean_names() %>%
  pivot_longer(cols = -c(province_state, country_region, lat, long), names_to = "date", values_to = "deaths") %>%
  select(country_region, date, deaths) 

global_deaths <- global_deaths %>% 
  mutate(sep_date = sub("x", "", date)) %>%
  mutate(new_date = as.Date(sep_date, format = "%m_%d_%y")) %>%
  group_by(country_region, new_date) %>%
  summarize(deaths = sum(deaths)) 

  #mutate(helper = c(
    #deaths[1],
   # deaths[1:(nrow(global_deaths) - 1)])
 # ) %>%
 # mutate(increment = deaths - helper) %>%
  #group_by(country_region)

# Recovered

global_recovered <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv")) %>% 
  clean_names() %>%
  pivot_longer(cols = -c(province_state, country_region, lat, long), names_to = "date", values_to = "recovered") %>%
  select(country_region, date, recovered)

global_recovered <- global_recovered %>% 
  mutate(sep_date = sub("x", "", date)) %>%
  mutate(new_date = as.Date(sep_date, format = "%m_%d_%y")) %>%
  group_by(country_region, new_date) %>%
  summarize(recovered = sum(recovered))

  #mutate(helper = c(
  #  recovered[1],
  #  recovered[1:(nrow(global_recovered) - 1)])
 # ) %>%
#  mutate(increment = recovered - helper) %>%
  #group_by(country_region)

# Join JHU data 

covidGlobal <- global_confirmed %>%
  inner_join(
    global_deaths, 
    by = c("country_region", "new_date"), 
    suffix = c("_confirmed", "_deaths")
  ) %>%
  inner_join(
    global_recovered, 
    by = c("country_region", "new_date"), 
    suffix = c("_confirmed", "_recovered")
  ) %>%
  select(
    country_region, 
    new_date, 
    confirmed, 
    #increment_confirmed, 
    deaths, 
   # increment_deaths, 
    recovered, 
   # increment
  ) %>% 
  rename(
    Country = country_region
  )

# Use countrycode package to standardize all country names, for easy joining
# with Oxford data (which comes with CountryCode column)

covidGlobal <- covidGlobal %>% 
  mutate(CountryCode = countrycode(Country, origin = 'country.name', destination = 'iso3c')) %>% 
  filter(Country != "Diamond Princess", Country != "MS Zaandam")

# Diamond Princess, Kosovo, MS Zaandam
```

```{r final data, include=FALSE}

# Join Oxford and JHU global data and clean

stringency <- oxford %>% 
  full_join(covidGlobal, by = c("CountryCode", "new_date")) %>% 
  filter(!is.na(confirmed)) %>% 
  select(
    Country, 
    CountryCode, 
    new_date, 
    S1_School.closing,
    S1_IsGeneral,
    S2_Workplace.closing,
    S2_IsGeneral,
    S3_Cancel.public.events,
    S3_IsGeneral,
    S4_Close.public.transport,
    S4_IsGeneral,
    S5_Public.information.campaigns,
    S5_IsGeneral,
    S6_Restrictions.on.internal.movement,
    S6_IsGeneral,
    S7_International.travel.controls,
    S8_Fiscal.measures,
    S9_Monetary.measures,
    S10_Emergency.investment.in.health.care,
    S11_Investment.in.Vaccines,
    S12_Testing.framework,
    S13_Contact.tracing,
    StringencyIndexForDisplay,
    confirmed,
   #increment_confirmed,
    deaths,
   # increment_deaths,
    recovered,
   # increment
    )
```

```{r regions, echo=FALSE}

regions <- read.csv(url("https://raw.githubusercontent.com/lukes/ISO-3166-Countries-with-Regional-Codes/master/all/all.csv")) %>% 
  select(name, region, sub.region) %>% 
  rename(Country = name) %>%
  mutate(CountryCode = countrycode(Country, origin = 'country.name', destination = 'iso3c')) 

# joining with existing dataset

stringency_regions <- stringency %>% 
  left_join(regions, by = "CountryCode")
```

```{r visualizations, echo=FALSE}

# S1-S7

# S8-S11

# S12-13

# Compare 

usa <- stringency_regions %>% 
  filter(CountryCode == "USA") %>% 
  filter(new_date > "2020-02-24") %>%
  ggplot(aes(x = new_date, color = as.factor(S6_Restrictions.on.internal.movement))) +
    geom_line(aes(y = confirmed), linetype = "solid" ) +
    geom_line(aes(y = deaths), linetype = "dashed") +
    geom_line(aes(y = recovered), linetype = "dotted") +
    # transition_reveal(new_date) +
    scale_color_manual(
      "", 
      breaks = c("0", "1", "2"),
      values = c("black", "darkred", "steelblue")
    ) +
    labs(
      title = "Spread and Stringency Response in USA",
      x = "Time",
      y = "Count"
    ) +
    scale_x_date(
      date_breaks = "1 week", 
      date_labels = "%b %d"
    ) +
  theme_minimal() 
usa
  
# Country-level - compare 2-3 side by side

# how to change background color over time, mapping to stringency
  
# Add animation
```

SelectInput() <- for country
DateRangeInput() <- for x axis 
SelectInput() <- for the policy measure

```{r}

 ## https://covidtracker.bsg.ox.ac.uk/stringency-scatter

# ideas: change the indices on the y-axis (S-1 : S-13); change the x-axis levels to confirmed, recovered, deaths
# figure out how to have time separate from plot (with a slider)
# how to highlight a certain country

# log transformation OR cases per capita

# Downloading population data from World Bank

population_data_18 <- read_csv("API_pop.csv", skip = 3) %>% 
  clean_names() %>% 
 select(country_code, x2018) %>% 
  rename(pop_2018 = x2018)

# join with population data and add log transformations (log base 10)

policy <- stringency_regions %>% 
  left_join(population_data_18, by = c("CountryCode" = "country_code")) %>% 
  mutate(confirmed_per_capita = confirmed / pop_2018,
         deaths_per_confirmed = deaths / confirmed,
         recovered_per_confirmed = recovered / confirmed) %>% 
  mutate(log_confirmed = log10(confirmed), 
         log_deaths = log10(deaths),
         log_recovered = log10(recovered))

# scatterplot

global_scatter <- policy %>% 
  filter(new_date == "2020-04-01") %>% 
  ggplot(aes(x = log_confirmed, y = StringencyIndexForDisplay, label = CountryCode)) +
    geom_point() +
    geom_text()
global_scatter

# regression: correlation between cases and stringency index

# add time as a factor 
# figure out how to select a certain country to be colored differently
# change log_confirmed to log_deaths and log_recovered

```


```{r regions, echo=FALSE}



```

```{r globalmap}
# https://covidtracker.bsg.ox.ac.uk/stringency-map

# figure out how to get the map --- leaflet
# https://bookdown.org/robinlovelace/geocompr/adv-map.html


# (hopefully get stringency as a continuous variable)




```

radioButtons ("caseInput", "Case Type",
              choices = c("Confirmed", "Deaths", "Recovered"),
              selected = "Confirmed")
              
selectInput ("indexInput", "Policy Measure",
              choices = c("School Closing", "Workplace Closing", "Public Events Cancellations",
              "Public Transport Closings", "Public Info Campaigns", "Restrictions on Internal Movement", "International Travel Controls", 
              "Fiscal Measures", "Monetary measures", "Emergency Investment in Healthcare", "Investment in Vaccines", "Testing Policy", "Contact Tracing"))
              
              
sliderInput("DatesMerge",
                          "Dates:",
                          min = as.Date("2020-01-22","%Y-%m-%d"),
                          max = Sys.Date(),
                          value=as.Date("2016-01-22"),
                          timeFormat="%Y-%m-%d")
                          
                          
output$globalpolicy <- renderPlot({
        if
        if
})
                          
                          
                          

output$gdp_graph <- renderPlot({
    if(input$gdp == "GDP") {
      y_value <- data$gdp
      y_lab <- "GDP"
      gdp_title <- "Number of Refugees and GDP"
    } 
    else if(input$gdp == "GDP Per Capita") {
      y_value <- data$gdp_percap
      y_lab <- "GDP Per Capita"
      gdp_title <- "Number of Refugees and GDP Per Capita"
    } else {
      y_value <- data$gdp_percap_growth
      y_lab <- "GDP Per Capita Growth Rate"
      gdp_title <- "Number of Refugees and GDP Per Capita Growth Rate"
    }
    
    # Use ggplot to create the framework for the graph. I used geom point to
    # make a scatter plot, geom smooth to add a line of best fit, and scale x
    # and y continuous to avoid the axies being in scientific notation because
    # it is not user friendly.
    
    data %>%
      ggplot(aes(refugee_number, y_value)) +
      geom_point() +
      scale_x_continuous(labels = scales::comma) +
      scale_y_continuous(labels = scales::comma) +
      geom_smooth(method = "lm") +
      labs(title = gdp_tit)

)



### S1: School closing (Record closings of schools and universities)
0 - no measures
1 - recommend closing
2 - require closing

### S2: Workplace closing (Record closings of workplaces)
0 - No measures
1 - recommend closing
2 - require closing

### S3: Cancel public events (Record cancelling public events)
0 - No measures
1 - Recommend cancelling
2 - Require cancelling

### S4: Close public transport (Record closing of public transport)
0 - No measures
1 - Recommend closing
2 - Require closing

### S5: Public info campaigns (Record presence of public info campaigns)
0 -No COVID-19 public information campaign
1 - COVID-19 public information campaign


### s6: Restrictions on internal movement (Record restrictions on internal movement)
0 - No measures
1 - recommend movement restriction
2 - restrict movement

### s7: International travel controls (Record restrictions on international travel)
0 - No measures
1 - Screening
2 - Quarantine on high-risk regions
3 - Ban on high-risk regions

### s8: Fiscal measures (What economic stimulus policies are adopted?)
Value of fiscal stimuli, including spending or tax cuts (in USD)

### s9: Monetary measures (What monetary policy interventions?)
Value of interest rate (in %)

### s10: Emergency investment in healthcare (Short-term spending on, e.g, hospitals, masks,etc)
Value of new short-term spending on health (in USD)

### s11: Investment in vaccines (Announced public spending on vaccine development)
Value of investment (in USD)

### S12: Testing policy (Who can get tested)
0 - No testing policy
1 - only testing those who both (a) have symptoms, and (b) meet specific criteria (eg key workers, admitted to hospital, came into contact with a known case, returned from overseas)
2 - testing of anyone showing COVID19 symptoms 
3 - open public testing (eg “drive through” testing available to asymptomatic people)

###S13: Contact tracing (Are governments doing contact tracing)


0 - no contact tracing
1 - limited contact tracing – not done for all cases
2 - comprehensive contact tracing – done for all cases